A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-29 rr-flow.Rmd
revised manuscript

>>>>

## Reproducing an Analysis

We provide a reproducible analysis as working example via github as a testbed for users. The example shows a minimalistic analysis of the 'Considerations of Future Consequences (CFC) Scale'. The analysis demonstrates a succesful implementation of our workflow including downloading external data, comparing their state using a checksum, and running a confirmatory factor analysis on the first few items using lavaan [@lavaan2012]. Once all mentioned tools are installed on a computer, the following few steps are necessary to reproduce our analysis:

```{bash}

TODO: Aaron

```
